---
title: "R Notebook"
output: html_notebook
---
The first step in this laboratory consisted in loading the igraph library, necessary for executing the graphs analysis.
```{r}
library(igraph)
```

Next we load the *ggplot2* library, in order to perform plots.
```{r}
library(ggplot2)
```

# Tasks
### 1. Plot the clustering coefficient and the average shortest-path as a function of the parameter p of the WS model.
```{r}
# Creation of the WS graph.
ws_graph <- watts.strogatz.game(1, 1000, 4, 0)
al0 = average.path.length(ws_graph) # Computing its avg path length using p = 0.
t0 = transitivity(ws_graph,type = "global") # Computing its transitivity using p = 0.
al = c(al0/al0) #Initializing the arrays.
t = c(mean_t0/mean_t0)
for(i in seq(0.001,1,0.001)){
    ws_graph <- watts.strogatz.game(1, 1000, 4, i)
    ali = average.path.length(ws_graph) #Computation of the new metrics.
    ti = transitivity(ws_graph,type = "global")
    al = append(al,ali/al0) # Storing the new normalized values.
    t = append(t,ti/t0)
}
```

Once the values are calculated, we proceed to plot them.
```{r}
plt1 = ggplot(as.data.frame(t),aes(seq(0,1,0.001))) +
geom_point(aes(y = t, colour = "Clustering Coefficient"))+
geom_point(aes(y = al, colour = "Average shortest path"))+
labs(x = "Probability", y = "") + scale_x_log10()+
ggtitle("Average shortest path and transitivity of a WS model")+  theme(plot.title = element_text(hjust = 0.5))

suppressWarnings(print(plt1))
```
### 3. Plot a histogram of the degree distribution of a BA network. What distribution does this follow? Can you describe it?

The first step for resolving this task consists in creating the graph.

```{r}
ba_graph <- barabasi.game(20000,m = 1)
```

Now we proceed to compute the histogram and the degree distribution using points.

```{r}
ggplot(as.data.frame(degree(ba_graph)), aes(x=`degree(ba_graph)`)) + geom_histogram(boundary = -0.5) +
labs(x = "Degree", y = "Frequency") +
ggtitle("Histogram of a BA model")+  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
degree_plot = ggplot(as.data.frame(degree.distribution(ba_graph)),aes(seq(0,10855,1))) +
geom_point(aes(y = `degree.distribution(ba_graph)`)) + 
labs(x = "Degree", y = "Relative frequency")+
ggtitle("Degree distribution of a BA model")+  theme(plot.title = element_text(hjust = 0.5))
degree_plot
```
To analyze if the BA degree distribution follows a powerlaw, we will perform a log-log plot of the axis.

To avoid numerical errors for performing the logarithm for values equal to 0, the addition of an epsilon has been performed.

```{r}
aux2 = as.data.frame(degree.distribution(ba_graph))
aux2$`degree.distribution(ba_graph)` = aux2$`degree.distribution(ba_graph)` + 10e-6
aux2
```


```{r}
ggplot(aux2,aes(seq(1,311,1))) +
geom_point(aes(y = `degree.distribution(ba_graph)`)) + 
labs(x = "Log Degree", y = "Log Relative frequency")+
ggtitle("Log Degree distribution of a BA model")+  theme(plot.title = element_text(hjust = 0.5)) +
scale_x_log10() + scale_y_log10()
```


